\documentclass{article}
\usepackage{tkz-euclide}
\input{../general}

\MakeTitle{1}

\begin{document}
\maketitle

\exerciseOld{0}{2}{1}
\begin{enumerate}
\item There exists a prime number such that if you divide it by 4 you have a remainder of 1 and it is not the sum of two squares.

\item There exists $x \in \mathbb{R}$ and $\epsilon > 0$ such that for all $\delta > 0$, there exists $y \in \mathbb{R}$, if $|y - x| < \delta$, then $|y^2 - x^2| \geq \epsilon$.

\item There exists $\epsilon > 0$ such that for all $\delta > 0$, there exist $x, y \in \mathbb{R}$ such that if $|y - x| < \delta$, then $|y^2 - x^2| \geq \delta$.
\end{enumerate}

\exerciseOld{0}{3}{1}
\begin{enumerate}
\item
$\begin{aligned}[t]
A * B    &= (E - A) \cap (E - B) = E - (A \cup B) \\
A \cup B &= E - (E - (A \cup B)) \\
         &= E - A * B \\
         &= (E - A * B) \cap (E - A * B) \\
         &= (A * B) * (A * B)
\end{aligned}$

\item
$\begin{aligned}[t]
A \cap B &= (E - (E - A)) \cap (E - (E - B)) \\
         &= (E - A) * (E - B) \\
         &= (A * A) * (B * B)
\end{aligned}$

\item
$\begin{aligned}[t]
E - A &= (E - A) \cap (E-A) \\
      &= A * A
\end{aligned}$
\end{enumerate}

\exerciseOld{0}{4}{6}
\begin{enumerate}
\item
$f$ can become one to one if it's domain is changed to $[0, \infty)$, namely, all nonnegative numbers. Then, for each $y \in [0, \infty)$, there is one and only one $x$ such that $y = f(x)$, which is $x = \sqrt{y}$.

$f$ cannot become one to one by solely changing its codomain. As long as its codomain contains any number other than 0, say $y$, there always exist two possible $x$ such that $f(x) = y$, namely $\sqrt{y}$ and $-\sqrt{y}$. If its codomain was changed to the singleton set $\{0\}$, the domain will also be changed to $\{0\}$. Hence it's impossible to make it one to one by by solely changing its codomain.

\item
For any real number $x$, as long as both $x$ and $-x$ are removed from $f$'s domain, for $y \in [0, \infty), y = x^2$, there doesn't exist $x'$ of $f$'s domain such that $f(x') = y$, because both two roots of the equation $y = x^2$ are removed from $f$'s domain. Hence, $f$ becomes not onto.

$f$ can become not onto if it's codomain is extended to contain negative real numbers. For every $y < 0$, there doesn't exist $x = \sqrt{y}$ such that $x$ is a real number.
\end{enumerate}

\exerciseOld{0}{4}{8}
\begin{enumerate}
\item $f^{-1}(A \cap B) = f^{-1}(A) \cap f^{-1}(B)$.

\Proof{} For every $x \in f^{-1}(A \cap B)$, there exists $y \in A \cap B$ such that $y = f(x)$. Because $y \in A$, $y \in B$, and $y = f(x)$, $x \in f^{-1}(A)$ and $x \in f^{-1}(B)$, or $x \in f^{-1}(A) \cap f^{-1}(B)$. Therefore, $f^{-1}(A \cap B) \subseteq f^{-1}(A) \cap f^{-1}(B)$.

For every $x \in f^{-1}(A) \cap f^{-1}(B)$, $x \in f^{-1}(A)$ and $x \in f^{-1}(b)$; as a result, there exist $y \in A$ and $z \in B$ such that $y = z = f(x)$, or, $y \in A \cap B$. By definition, $x \in f^{-1}(A \cap B)$. So, $f^{-1}(A) \cap f^{-1}(B) \subseteq f^{-1}(A \cap B)$. Since two sets are subsets of each other, they are equal. \QED

\item $f^{-1}(A \cup B) = f^{-1}(A) \cup f^{-1}(B)$.

\Proof{} For every $x \in f^{-1}(A \cup B)$, there exists $y \in A \cup B$ such that $y = f(x)$. Because $y$ is an element of either $A$ or $B$ or both, $x$ is the element of $f^{-1}(A)$ and $x \in f^{-1}(B)$ or both, which means $x \in f^{-1}(A) \cup f^{-1}(B)$. Therefore, $f^{-1}(A \cup B) \subseteq f^{-1}(A) \cup f^{-1}(B)$.

For every $x \in f^{-1}(A) \cup f^{-1}(B)$, $x \in f^{-1}(A)$ or $x \in f^{-1}(b)$ or both. If $x \in f^{-1}(A)$, there exists $y \in A$ such that $y = f(x)$; then, $y \in A \cup B$, $x \in f^{-1}(A \cup B)$ by definition. Similarly, if $x \in f^{-1}(B)$, $x$ will also be an element of $f^{-1}(A \cup B)$. So, $f^{-1}(A) \cup f^{-1}(B) \subseteq f^{-1}(A \cup B)$. Since two sets are subsets of each other, they are equal. \QED
\end{enumerate}

\exerciseOld{0}{4}{10}
\begin{enumerate}
\item Let the function \FunSS{f}{B}{C} and \FunSS{g}{A}{B} be onto. Then the composition $f \circ g$ is onto.

\Proof{} For every $c \in C$: since \FunSS{f}{B}{C} is surjective, there exists $b \in B$ such that $f(b) = c$; since \FunSS{g}{A}{B} is surjective, there exists $a \in A$ such that $g(a) = b$. Therefore, for every $c \in C$, there exists $a \in A$ such that $(f \circ g)(a) = f(g(a)) = c$. Thus, $f \circ g$ is surjective, or onto. \QED

\item Let the function \FunSS{f}{B}{C} and \FunSS{g}{A}{B} be one to one. Then the composition $f \circ g$ is one to one.

\Proof{} For every $c \in C$, since \FunSS{f}{B}{C} is injective, there exists at most one $b \in B$ such that $f(b) = c$; if such $b$ doesn't exist for this $c$, there doesn't exist $a \in A$ such that $f(g(a)) = c$; if such $b$ does exists, then since \FunSS{g}{A}{B} is also injective, there exists at most one $a \in A$ such that $g(a) = b$. Therefore, for every $c \in C$, there exists zero or one $a \in A$ such that $(f \circ g)(a) = f(g(a)) = c$. Thus, $f \circ g$ is injective, or one to one. \QED
\end{enumerate}

\exerciseOld{0}{4}{12}
Let $F$ be a sequence of functions:
$$\begin{array}{rcl}
F_0 &=& \ln \\
F_1 &=& \ln \circ \ln \\
F_2 &=& \ln \circ \ln \circ \ln \\
F_3 &=& \ln \circ \ln \circ \ln \circ \ln \\
&\vdots& \\
F_n &=& \ln \text{composed with itself $n$ times}
\end{array}$$

Let $X_n$ be the (natural) domain of $F_{n}$. $X_{0}$ is the domain of $\ln$, namely $(0, \infty)$. For each $n \in \mathbb{N}$, $F_{n+1} = F_n \circ \ln$, $X_{n+1}$ is the intersection of the inverse image of $X_n$ under $\ln$ and $\ln$'s domain $(0, \infty)$. The inverse image of a set $X$ under $\ln$ is also the image of $X$ under the inverse function of $\ln$, namely $exp(x) = e^x$. Note that $exp$ is a monotonically increasing function.

\begin{enumerate}
\item $\ln \circ \ln = F_1 = F_0 \circ \ln$.

$X_0 = (0, \infty)$, and its image under $exp$ is $(exp(0), exp(\infty)) = (1, \infty)$. The natural domain of this function is $X_1 = (1, \infty) \cap (0, \infty) = (1, \infty)$.

\item $\ln \circ \ln \circ \ln = F_2 = F_1 \circ \ln$

$X_1 = (1, \infty)$, and its image under $exp$ is $(exp(1), exp(\infty)) = (e, \infty)$. The natural domain of this function is $X_2 = (e, \infty) \cap (0, \infty) = (e, \infty)$.

\item $\ln$ composed with itself $n$ times $= F_n = F_{n - 1} \circ \ln$

A function \FunSS{ans}{\mathbb{Z}^+}{\mathbb{R}} can be defined as:
$$ans(x) = \left\{
\begin{array}{lc}
1            & x = 1 \\
e^{ans(x-1)} & x > 1
\end{array}
\right.$$.

Or tetration of $e$:
$$ans(x) = {^{n}e} = \underbrace{e^{e^{\cdot^{\cdot^{e}}}}}_n$$

Assume that for every positive integer $i$, $X_i = (ans(i), \infty)$. This can be proven inductively as $X_1 = (ans(1), \infty)$, $X_2 = (ans(2), \infty)$, and $X_i = (exp(ans(i-1)), exp(\infty)) \cap (0, \infty) = (ans(i), \infty)$. Therefore, the natural domain of $F_n$, or $\ln$ composed with itself $n$ times, is $X_n = (ans(n), \infty)$.
\end{enumerate}


\input{sec0101}
\input{sec0102}

\end{document}
